Redundant calibration as a complex optimization problem

### 2017-01-13 paper.tex
more chicken egg corrections

Recall, that \citet{Smirnov2015} showed that \textsc{StEfCal} can also be derived by approximating the $\bH$, associated with skymodel-based calibration, with 
its diagonal. We will now use the diagonal approximation approach presented in \citet{Smirnov2015} to yet again re-derive the redundant calibration algorithm presented in \citet{Marthi2014}.

@@

Lastly, we showed how \citet{Marthi2014}, \citet{Salvini2014} and \citet{Smirnov2015} relate to each other (see Section~\ref{sec:red_c}). The ADI method associated with skymodel-based calibration (i.e. \textsc{StEfCal}) is presented
in \citet{Salvini2014}. \citet{Smirnov2015} showed that it is possible to rederive this skymodel-based ADI method through complex optimization. In particular, they showed that if 
we approximate the $\bH$ associated with the LM algorithm with its diagonal then we can rederive the ADI update rules presented in \citet{Salvini2014}. 
\citet{Marthi2014} applied the ADI method to the redundant use case. This fact is not immediatly clear when inspecting \citet{Marthi2014}. The ADI update rules presented \citet{Marthi2014} were derived by taking the partial derivatives of 
the objective function towards the unknown parameters, setting the intermediate results to zero and then solving for the unknowns. In this paper we show that 
these same ADI update rules can be derived using the diagonal approximation technique proposed in \citet{Smirnov2015}. The fact that we can use this diagonal approximation
technique to derive these update rules imply that the algorithm presented in \citet{Marthi2014} is in fact the ADI method (i.e. redundant \textsc{StEfCal}). This same
fact can be established by directly applying the skymodel-based ADI derivation presented in \citet{Salvini2014} to the redundant use case.

>>>>

Recall, that \citet{Smirnov2015} showed that \textsc{StEfCal} can also be derived by approximating the $\bH$, associated with skymodel-based calibration, with 
its diagonal. To double check if our statement that the algorithm in \citet{Marthi2014} is in actual fact redundant \textsc{StEfCal} (i.e. some kind of ADI method) we will now use the diagonal approximation approach presented in \citet{Smirnov2015} to yet again re-derive the redundant calibration algorithm presented in \citet{Marthi2014}.

@@

Lastly, we showed how \citet{Marthi2014}, \citet{Salvini2014} and \citet{Smirnov2015} relate to each other (see Section~\ref{sec:red_c}). The ADI method associated with skymodel-based calibration (i.e. \textsc{StEfCal}) is presented
in \citet{Salvini2014}. \citet{Smirnov2015} showed that it is possible to re-derive this skymodel-based ADI method through complex optimization. In particular, they showed that if 
we approximate the $\bH$ associated with the LM algorithm with its diagonal then we can rederive the ADI update rules presented in \citet{Salvini2014}. 
\citet{Marthi2014} actually proposes to use the ADI method to perform redundant calibration. This fact is not immediately clear when superficially inspecting \citet{Marthi2014}. The redundant calibration algorithm presented in \citet{Marthi2014} was derived by taking the partial derivatives of 
the objective function towards the unknown parameters, setting the intermediate results to zero and then solving for the unknowns. In Section~\ref{sec:red_c}, we showed that 
this algorithm is in actual fact an extension of the skymodel-based ADI method presented in \citet{Salvini2014} to the redundant calibration use case (i.e. we showed that this algorithm is in actual fact redundant \textsc{StEfCal}).
We also re-derived the aforementioned redundant calibration algorithm by applying the diagonal approximation approach presented in \citet{Smirnov2015}, which serves as yet another additional confirmation  
that this algorithm is in fact redundant \textsc{StEfCal} (i.e. that it is some kind of ADI method).
